---
title: "Investigate RK's JN code"
output: html_notebook
---


```{r}
load("V:Research/Papers/SOR.NSUTx/SUTx.w123456.RData")
```

```{r}
save.image("V:Research/Papers/SOR.NSUTx/SUTx.w123456.RData")
```

```{r}
packages <- c("data.table", "keyring", "blastula",
              "tidyverse", "dtplyr", "naniar",
              "network", "sna", "RHNetTools", "Matrix", "RSiena", 
              "JMLUtils", "haven", "glue")
if(length(setdiff(packages, rownames(installed.packages))) > 0) {
  lapply(packages, library, character.only = TRUE)
}
# If necessary (RSienaTest is not on Cran):
#install.packages("RSienaTest", repos="http://R-Forge.R-project.org")
workingDir <- here::here()
```


```{r}
Mod48<- readRDS("V:/Research/Papers/SOR.NSUTx/Mod48.RDS")
```

#Mod 48 (test model)
```{r}
print(Mod48)
tM <- Mod48
```

RFEgo (12) is g1 (primary)
RFAlt (11) is moderator (g2)
RFEgo x RFAlt (13) is interac term

NOTE: when you specify the covariance between g1 and g3, be sure it's above the diagonal
so, the row should always be LESS THAN the column!!)
#Ego (12) is primary, alt(11) is mod
```{r}
mod <- tM
g1 <- mod$theta[12] #Beta: primary (ego)
g2 <- mod$theta[11] #Beta: moderator (alt)
g3 <- mod$theta[13] #Beta: interaction
g1Var <- mod$covtheta[12,12] #Var primary
g2Var <- mod$covtheta[11,11] #Var moderator
g3Var <- mod$covtheta[13,13] #Var (prim x mod)
g1g3Cov <-mod$covtheta[12,13] #Cov(prim, int)
tSq <- 1.96*1.96 #squared critical value (for .05 2-tailed)
```
Calculate quadratic coefficients ac, bc, cc
```{r}
ax <- (tSq*g3Var) - g3^2
bx <- 2*((tSq*g1g3Cov) - (g1*g3))
cx <- (tSq*g1Var) - g1^2
# Will the equation have real roots?
isThisPos<-(bx^2)-(4*ax*cx) #If it isn't, the equation has no real roots.
ax
bx 
cx
```

Quadratic formula
```{r}
rootPos.ep <- (-bx + sqrt((bx^2)-(4*ax*cx)))/(2*ax)
rootNeg.ep <- (-bx - sqrt((bx^2)-(4*ax*cx)))/(2*ax)
```

rootPos.ep = -3.615 
rootNeg.ep =  0.850 

###Check ep eq roots.
The equation is:
$$f(e)= -0.03068*e^2 - 0.08484*e + 0.09425 = 0$$
This calculation should be 0 for either 
rootPos or rootNeg. Both are. 
```{r}
ax*(rootNeg.ep^2) + (bx*rootNeg.ep) + cx
ax*(rootPos.ep^2) + (bx*rootPos.ep) + cx
```
###JNSiena on same model
```{r}
JNSiena(siena07out = tM,
        theta1=12, #ego is primary in 1st dataframe
        theta2=11, #alt is moderator in 1st dataframe
        thetaInt = 13,
        theta1vals = c(-3.7, 0.5, 0.6, 0.7, 0.8, 0.9,  1),
        theta2vals = c(-3.7, 0.5, 0.6, 0.7, 0.8, 0.9,  1),
        alpha=0.05
        )
```


#Alt (11) is primary, ego (12) is mod
RFAlt (11) is g1 (primary)
RFEgo (12) is moderator (g2)
RFEgo x RFAlt (13) is interac term
```{r}
mod <- tM
g1 <- mod$theta[11] #Beta: primary (alt)
g2 <- mod$theta[12] #Beta: moderator (ego)
g3 <- mod$theta[13] #Beta: interaction
g1Var <- mod$covtheta[11,11] #Var primary
g2Var <- mod$covtheta[12,12] #Var moderator
g3Var <- mod$covtheta[13,13] #Var (prim x mod)
g1g3Cov <-mod$covtheta[11,13] #Cov(prim, int)
tSq <- 1.96*1.96 #squared critical value (for .05 2-tailed)
```
Calculate quadratic coefficients ax, bx, cx
```{r}
ax <- (tSq*g3Var) - g3^2
bx <- 2*((tSq*g1g3Cov) - (g1*g3))
cx <- (tSq*g1Var) - g1^2
# Will the equation have real roots?
isThisPos<-(bx^2)-(4*ax*cx) #If it isn't, the equation has no real roots.
ax
bx 
cx
```

Quadratic formula
```{r}
rootPos.ap <- (-bx + sqrt((bx^2)-(4*ax*cx)))/(2*ax)
rootNeg.ap <- (-bx - sqrt((bx^2)-(4*ax*cx)))/(2*ax)
```
rootPos.ap = -4.88
rootNeg.ap =  0.604 



