---
title: "Draft of Package Upgrade for New Major R Version"
output: html_notebook
---

Here is the procedure:
1. With the old version of R running (either before you install the new
   version, or after but selecting the old version in Tools/Project Options),
   run this next chunk:

```{r}
#Gets character vector of all installed package names 
packs <- installed.packages()[,1] 
#Write named character vector into .r file
sink("packs2move.r", append=F, split=F)
dput(packs)
sink()
```

2. Install (if necessary) and activate the new version of R. Normally the new
   version will boot up automatically after it's installed, but you can also
   manually select in in the Tools/Project Options menu).

3. Run the next chunk. This will install the packages in the new pkg lib
   directory. 
   a. In response to the offer to "restart R" because one of the packages is
      already loaded, just say NO. 
   b. When it offers to install from source and compile, say YES.
   
If there are a lot of packages, the recompliation process will take a good
while to finish.
 
```{r}
pax <- unlist(source("packs2move.r"))
pax <- pax[1:length(pax)-1] #Removes extraneous list item
install.packages(pax)
```



```{r}
candidates <- c( Sys.getenv("R_PROFILE"),
                 file.path(Sys.getenv("R_HOME"), "etc", "Rprofile.site"),
                 Sys.getenv("R_PROFILE_USER"),
                 file.path(getwd(), ".Rprofile") )

Filter(file.exists, candidates)
```

Additional Notes:

If necessary (usually only if a major R upgrade, e.g. from v. 4.x to version 5.x
 etc. be sure to upgrade your development tools, so
 you'll be able to build all the packages in the new R version.
 see here for doc:
https://support.rstudio.com/hc/en-us/articles/200486498-Package-Development-Prerequisites
 Basically if there is a new version of RTools, download and install from here:
 https://cran.rstudio.com/bin/windows/Rtools/.
Then make sure it's on system PATH per doc recommendations 
I don't think you need devtools available in the new version to make this work, 
 but you might. In that case, you'll need to install that first, manually, 
 and then go from there. Check this link:
https://www.r-project.org/nosvn/pandoc/devtools.html

